Generalized Bradley-Terry models

### 2025-04-01 inst/jss_hyper3_real.Rnw
fig = TRUE needed

\begin{figure}[htbp]
  \begin{center}
<<plotproflikeoldfirm, echo=FALSE>>=
plot(lam, logLike - max(logLike), type = 'b')
abline(v = 1, col = 'gray')
segments(x0 = 1.785, y0 = 0.1, y1 = -1, col = 'red')
abline(h = c(0, -2), col = 'gray')
@
\caption{A\label{profilesupportlambda} profile support function for
  the home-team advantage $\lambda$.  Vertical gray line shows
  $H_0\colon\lambda =1$, horizontal lines show the
  two-units-of-support limits; small red bar shows
  $\hat{\lambda}\simeq 1.785$}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
<<docontourplot, cache = FALSE>>=
contour(lambda, D, matrix(LL, n, n), levels = -2*(1:9),
        xlab = expression(lambda), ylab = expression(D))
points(maxv[1], maxv[2], pch = 16, col = 'red')
abline(v=1, col = 'gray')
@
\caption{Contours of support\label{contourlambdaD} evaluated over
  a grid.  Maximum likelihood estimate for $(\lambda, D)$ shown as
  a red dot at the evaluate.  Vertical gray line shows $H_0\colon\lambda=1$}
  \end{center}
\end{figure}

>>>>

\begin{figure}[htbp]
  \begin{center}
<<plotproflikeoldfirm, echo=FALSE, fig = TRUE>>=
plot(lam, logLike - max(logLike), type = 'b')
abline(v = 1, col = 'gray')
segments(x0 = 1.785, y0 = 0.1, y1 = -1, col = 'red')
abline(h = c(0, -2), col = 'gray')
@
\caption{A\label{profilesupportlambda} profile support function for
  the home-team advantage $\lambda$.  Vertical gray line shows
  $H_0\colon\lambda =1$, horizontal lines show the
  two-units-of-support limits; small red bar shows
  $\hat{\lambda}\simeq 1.785$}
\end{center}
\end{figure}

@@

\begin{figure}[htbp]
  \begin{center}
<<docontourplot, cache = FALSE, fig = TRUE>>=
contour(lambda, D, matrix(LL, n, n), levels = -2*(1:9),
        xlab = expression(lambda), ylab = expression(D))
points(maxv[1], maxv[2], pch = 16, col = 'red')
abline(v=1, col = 'gray')
@
\caption{Contours of support\label{contourlambdaD} evaluated over
  a grid.  Maximum likelihood estimate for $(\lambda, D)$ shown as
  a red dot at the evaluate.  Vertical gray line shows $H_0\colon\lambda=1$}
  \end{center}
\end{figure}
